Pervasive duplication of tumor suppressor genes preceded parallel evolution

### 2020-06-04 paper_PLOS/paper_PLOS_draft.Rmd
New double-tree figures

set.seed(1234)
suppressMessages(suppressWarnings(require(data.table)))
suppressMessages(suppressWarnings(require(tidyverse)))
options(readr.num_columns = 0)
suppressMessages(suppressWarnings(require(ape)))
suppressMessages(suppressWarnings(require(geiger)))
suppressMessages(suppressWarnings(require(nlme)))
suppressMessages(suppressWarnings(require(treeio)))
suppressMessages(suppressWarnings(require(tidytree)))
suppressMessages(suppressWarnings(require(ggtree)))
suppressMessages(suppressWarnings(require(ggimage)))
suppressMessages(suppressWarnings(require(ggpubr)))
suppressMessages(suppressWarnings(require(ggsci)))
suppressMessages(suppressWarnings(require(plotly)))
suppressMessages(suppressWarnings(require(ggplotify)))
suppressMessages(suppressWarnings(require(UpSetR)))
suppressMessages(suppressWarnings(require(ggrepel)))
suppressMessages(suppressWarnings(require(magick)))
suppressMessages(suppressWarnings(require(ggrepel)))
suppressMessages(suppressWarnings(require(gghighlight)))
suppressMessages(suppressWarnings(require(broom.mixed)))
suppressMessages(suppressWarnings(require(purrr)))
suppressMessages(suppressWarnings(require(kableExtra)))
suppressMessages(suppressWarnings(require(stargazer)))
source("../code/generalFunctions.R")
```
```{r Data Files, include = F}
UP000005640 <- read_tsv("../data/input/UP000005640.withheader.tsv")
gene_list <- read_lines("../output/recBlastDBPrep/AvA_geneList.txt")
gene_list_filtered <- read_lines("../output/recBlastDBPrep/AvA_geneList_filtered.txt")
genomeTable <- read_csv("../output/other/genomeTable.csv")

@@

>>>>

set.seed(1234)
suppressMessages(suppressWarnings(require(data.table)))
suppressMessages(suppressWarnings(require(tidyverse)))
options(readr.num_columns = 0)
suppressMessages(suppressWarnings(require(ape)))
suppressMessages(suppressWarnings(require(geiger)))
suppressMessages(suppressWarnings(require(nlme)))
suppressMessages(suppressWarnings(require(treeio)))
suppressMessages(suppressWarnings(require(tidytree)))
suppressMessages(suppressWarnings(require(ggtree)))
suppressMessages(suppressWarnings(require(ggimage)))
suppressMessages(suppressWarnings(require(ggpubr)))
suppressMessages(suppressWarnings(require(ggsci)))
suppressMessages(suppressWarnings(require(plotly)))
suppressMessages(suppressWarnings(require(ggplotify)))
suppressMessages(suppressWarnings(require(UpSetR)))
suppressMessages(suppressWarnings(require(ggrepel)))
suppressMessages(suppressWarnings(require(magick)))
suppressMessages(suppressWarnings(require(ggrepel)))
suppressMessages(suppressWarnings(require(gghighlight)))
suppressMessages(suppressWarnings(require(broom.mixed)))
suppressMessages(suppressWarnings(require(purrr)))
suppressMessages(suppressWarnings(require(kableExtra)))
suppressMessages(suppressWarnings(require(stargazer)))
suppressMessages(suppressWarnings(require(ggnewscale)))
source("../code/generalFunctions.R")
```
```{r Data Files, include = F}
UP000005640 <- read_tsv("../data/input/UP000005640.withheader.tsv")
gene_list <- read_lines("../output/recBlastDBPrep/AvA_geneList.txt")
gene_list_filtered <- read_lines("../output/recBlastDBPrep/AvA_geneList_filtered.txt")
genomeTable <- read_csv("../output/other/genomeTable.csv")

@@

```{r Figure-DoubleTree-Bodysize-CancerSuscept-Genomes}

### Body Size ###
bsize.Atlantogenata.table <- bsize.Atlantogenata %>% as_tibble
bsize.Atlantogenata.table[which(bsize.Atlantogenata.table$node == MRCA(bsize.Atlantogenata, "Pseudoungulata", "Elephantulus.edwardii")),]$label <- "Afroinsectivora"
bsize.Atlantogenata <- bsize.Atlantogenata.table %>% as.treedata()

lnsize.bsize.Atlantogenata <- bsize.Atlantogenata %>% as_tibble() %>% select(label, Species.strict, lnSize)
bsize.Atlantogenata.genomes <-  bsize.Atlantogenata@phylo %>% 
  treeio::drop.tip(bsize.Atlantogenata@phylo$tip.label[!bsize.Atlantogenata@phylo$tip.label %in% genomeTable.atlantogenata$label]) %>% as.tibble
bsize.Atlantogenata.genomes <- left_join(bsize.Atlantogenata.genomes, lnsize.bsize.Atlantogenata) %>% as.treedata

p.tree.atlantogenata.genomes <- bsize.Atlantogenata.genomes %>% 
  ggtree(
    aes(color=as.numeric(lnSize))
  )

### Cancer Suscept ###
tree.cancerSucceptibility.Atlantogenata.table <- tree.cancerSucceptibility.Atlantogenata %>% as_tibble
tree.cancerSucceptibility.Atlantogenata.table[which(tree.cancerSucceptibility.Atlantogenata.table$node == MRCA(tree.cancerSucceptibility.Atlantogenata, "Pseudoungulata", "Elephantulus edwardii")),]$label <- "Afroinsectivora"
tree.cancerSucceptibility.Atlantogenata <- tree.cancerSucceptibility.Atlantogenata.table %>% as.treedata()

cancerSucceptibility.Atlantogenata.genomes <- tree.cancerSucceptibility.Atlantogenata %>% 
  as_tibble() %>%  
  mutate(abslog2CancerSucceptabilityChange = log2CancerSucceptabilityChange %>% abs(), 
         branch.length=abslog2CancerSucceptabilityChange) %>% 
  select(label, abslog2CancerSucceptabilityChange, log2CancerSucceptabilityChange, lnK1)
tree.cancerSucceptibility.Atlantogenata.genomes <-  tree.cancerSucceptibility.Atlantogenata %>% 
  as_tibble %>% 
  filter(!is.na(node)) %>%  
  mutate(branch.length = log2CancerSucceptabilityChange %>% abs()) %>% 
  as.treedata %>% 
  as.phylo() %>% 
  treeio::drop.tip(tree.cancerSucceptibility.Atlantogenata@phylo$tip.label[!tree.cancerSucceptibility.Atlantogenata@phylo$tip.label %in% genomeTable.atlantogenata$Species.strict])  %>% as.tibble
tree.cancerSucceptibility.Atlantogenata.genomes <- left_join(tree.cancerSucceptibility.Atlantogenata.genomes, cancerSucceptibility.Atlantogenata.genomes) %>% as.treedata

p.tree.cancerSucceptibility.Atlantogenata.genomes <- tree.cancerSucceptibility.Atlantogenata.genomes %>% 
  ggtree(
    aes(color=as.numeric(abslog2CancerSucceptabilityChange))
  )

### Double Tree ###

d.dbltree.1 <- p.tree.atlantogenata.genomes$data
d.dbltree.2 <- p.tree.cancerSucceptibility.Atlantogenata.genomes$data

d.dbltree.2$x <- max(d.dbltree.2$x) - d.dbltree.2$x + max(d.dbltree.1$x) + 500

p.dbltree <-
  bsize.Atlantogenata.genomes %>% 
  ggtree(., aes(color=lnSize), size=2) +
  scale_color_viridis_c(option = "A") + 
  geom_nodepoint(size=2) + 
  geom_tippoint(size=2) +
  geom_tiplab(x=(min(d.dbltree.2$x)+max(d.dbltree.1$x))/2, color="black", hjust = 0.5) +
  new_scale_color() + 
  geom_tree(data=d.dbltree.2, aes(color=log2CancerSucceptabilityChange), inherit.aes = F, size=2) + 
  geom_nodepoint(data=d.dbltree.2, aes(color=log2CancerSucceptabilityChange, x=x, y=y), inherit.aes = F, size=2) + 
  geom_tippoint(data=d.dbltree.2, aes(color=log2CancerSucceptabilityChange, x=x, y=y), inherit.aes = F, size=2) +
  # scale_color_viridis_c(option = "D") + 
    scale_color_distiller(palette = "YlGnBu")+
    theme(
      plot.background = element_rect(fill="grey"),
      panel.background = element_rect(fill="grey"),
      legend.background = element_rect(fill="grey")
    )

  p.dbltree
```

```{r Figure-DoubleTree-Bodysize-CancerSuscept-All}

### Body Size ###

p.tree.atlantogenata.genomes <- bsize.Atlantogenata %>% 
  ggtree(
    aes(color=as.numeric(lnSize))
  )

### Cancer Suscept ###

tree.cancerSucceptibility.Atlantogenata <-  tree.cancerSucceptibility.Atlantogenata %>% 
  as_tibble %>% 
  filter(!is.na(node)) %>%  
  mutate(branch.length = log2CancerSucceptabilityChange %>% abs()) %>% 
  as.treedata

p.tree.cancerSucceptibility.Atlantogenata.2 <- tree.cancerSucceptibility.Atlantogenata %>% 
  ggtree(
    aes(color=as.numeric(log2CancerSucceptabilityChange))
  )

### Double Tree ###

d.dbltree.3 <- p.tree.atlantogenata.genomes$data
d.dbltree.4 <- p.tree.cancerSucceptibility.Atlantogenata.2$data

d.dbltree.4$x <- max(d.dbltree.4$x) - d.dbltree.4$x + max(d.dbltree.3$x) + 500

p.dbltree.all <-
  bsize.Atlantogenata %>% 
  ggtree(., aes(color=lnSize), size=1) +
  scale_color_viridis_c(option = "A") + 
  geom_nodepoint(size=2) + 
  geom_tippoint(size=2) +
  geom_tiplab(x=(min(d.dbltree.4$x)+max(d.dbltree.3$x))/2, color="black", hjust = 0.5) +
  new_scale_color() + 
  geom_tree(data=d.dbltree.4, aes(color=log2CancerSucceptabilityChange), inherit.aes = F, size=1) + 
  geom_nodepoint(data=d.dbltree.4, aes(color=log2CancerSucceptabilityChange, x=x, y=y), inherit.aes = F, size=2) + 
  geom_tippoint(data=d.dbltree.4, aes(color=log2CancerSucceptabilityChange, x=x, y=y), inherit.aes = F, size=2) +
  # scale_color_viridis_c(option = "D") + 
    scale_color_distiller(palette = "YlGnBu")+
    theme(
      plot.background = element_rect(fill="grey"),
      panel.background = element_rect(fill="grey"),
      legend.background = element_rect(fill="grey")
    )

  p.dbltree.all
```
